Capturing Policies for BYOD

### 2016-10-25 paper.tex
updates

\usepackage{microtype}
\usepackage{amsmath,amssymb,mathtools}

@@

\usepackage{listings}
\lstdefinelanguage{AppPAL}{%
  morekeywords={if,inf,says,where,true,false,with,is},
  otherkeywords={can-act-as,can-say},
  sensitive=true,
  morestring=[b]',
  literate={\ inf\ }{{$\infty$}}5
}[keywords,strings]
\lstset{%
  basicstyle=\ttfamily,
  keywordstyle=\ttfamily\slshape,
  stringstyle=\sffamily,
  columns=flexible,
  mathescape,
  tabsize=2,
  showstringspaces=true,
  %numbers=left,
  breaklines=true,
  numberstyle=\tiny\ttfamily\color{Gray},
  commentstyle=\ttfamily\color{Gray}
}
\newcommand{\code}[2][]{\lstinline[breaklines=true, #1]{#2}}

@@

@@

@@

We analysed five different policies to find common idioms.
The first is the \emph{Security Policy Template: Use of Handheld Devices in a Corporate Environment}, published by the SANS Institute~\cite{nicholas_r._c._guerin_security_2008}.
This is a hypothetical policy published to help companies mitigate the threats to corporate assets caused by mobile devices. 
Companies are expected to modify the document to suit their needs.  The policy is general; not specific to any particular industry, device, or country's legislation.
The second is taken from Healthcare Information Management System Society~\cite{healthcare_information_and_management_systems_society_mobile_2012}; a US non-profit company trying to improve healthcare through IT.  
The policy is designed as a sample agreement for a system trying to manage personal mobile devices in a healthcare environment.
The third is taken from an british hospital trust~\cite{kennington_mobiles_2014}, and describes the BYOD scheme used in practice at the hospital. 
Finally two simpler policies are taken from Edinburgh university~\cite{david_williamson_bring_2015} and a company specialising in emergency sirens~\cite{code3pse.org_sample_????}. 
These policies are simpler than the other comprised of much more general rules and only a page or two in length.

\begin{itemize}
  \item SANS
  \item NHS
  \item HiMMS
  \item Edinburgh
  \item Code3SPE
\end{itemize}
\todo{Describe differences and similaritites at a high level between these policies.}

>>>>

\usepackage{microtype}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{hyperref}
\usepackage{booktabs}

@@

\usepackage{listings}
\lstdefinelanguage{AppPAL}{%
  morekeywords={if,inf,says,where,true,false,with,is},
  otherkeywords={can-act-as,can-say},
  sensitive=true,
  morestring=[b]',
  literate={\ inf\ }{{$\infty$}}5
}[keywords,strings]
\lstset{%
  basicstyle=\ttfamily,
  keywordstyle=\ttfamily\slshape,
  stringstyle=\sffamily,
  columns=flexible,
  mathescape,
  tabsize=2,
  showstringspaces=true,
  %numbers=left,
  frame=single,
  breaklines=true,
  numberstyle=\tiny\ttfamily\color{Gray},
  commentstyle=\ttfamily\color{Gray}
}
\newcommand{\code}[2][]{\lstinline[breaklines=true, #1]{#2}}

@@

\newenvironment{policyrule}[1]{%
  \begin{framed}
      \noindent\textbf{\sffamily #1}:~\itshape
}{
  \end{framed}
}

@@

\subsection{Changes to AppPAL}

We have used AppPAL to formalise the BYOD policies.
AppPAL is an instantiation of Becker's SecPAL~\cite{becker_secpal:_2010} we have previously used to describe app privacy preferences~\cite{hallett_apppal_2016}.
To describe BYOD policies we have extended AppPAL with types.
This allows our policies to be more succinct and readable whilst losing none of the expressive power.
When describing variables in the head of an AppPAL assertion.

@@

We analysed five different policies to find common idioms.
The first is the \emph{Security Policy Template: Use of Handheld Devices in a Corporate Environment}, published by the SANS Institute~\cite{nicholas_r._c._guerin_security_2008}.
This is a hypothetical policy published to help companies mitigate the threats to corporate assets caused by mobile devices. 
Companies are expected to modify the document to suit their needs.  
The policy is general; not specific to any particular industry, device, or country's legislation.
The second is taken from Healthcare Information Management System Society~\cite{healthcare_information_and_management_systems_society_mobile_2012}; 
  a US non-profit company trying to improve healthcare through IT.  
It is relatively short but interesting because it contains concerns specific to healthcare scenarios, and is written as a contract the users are agreeing to follow. 
In contrast every other policy we looked at is written as a series of rules users should follow to ensure compliance.
The policy is designed as a sample agreement for a system trying to manage personal mobile devices in a healthcare environment.
The third is taken from an british hospital trust~\cite{kennington_mobiles_2014}, and describes the BYOD scheme used in practice at the hospital. 
Finally two simpler policies are taken from Edinburgh university~\cite{david_williamson_bring_2015} and a company specialising in emergency sirens~\cite{code3pse.org_sample_????}. 
These policies are simpler than the other comprised of much more general rules and only a page or two in length.

\begin{table}\centering\footnotesize\sffamily
  \begin{tabular}{l c c c c c}
    \toprule
                             & {SANS}       & {HiMSS}     & {NHS}       & {Edinburgh} & {Sirens}    \\
    \midrule
    Number of rules          & 33           & 15          & 56          &             & 25          \\
    SecPAL assertions        & 71           & 21          & 58          & 10          & 39          \\
    Policy coverage          & 33 (100$\%$) & 14 (93$\%$) & 40 (71$\%$) &             & 22 (88$\%$) \\
    \midrule
    Delegations              & 23           & 5           & 33          & 2           & 13          \\
    Acknowledgement          &              &             &             &             &             \\
    Partial Acknowledgement  &              &             &             &             &             \\
    \bottomrule             \\
  \end{tabular}
  \label{tab:summary}
  \caption{Summary of the contents of each of the BYOD policies.}
\end{table}

The policies are summarised in \autoref{tab:summary}.
Each policy contains a series of \emph{rules}, which are implemented by one or more \emph{AppPAL assertions}.
The \emph{policy coverage} represents the number of rules that have an AppPAL description attached.
Not all the rules in a policy require an AppPAL translation.
For example rule 9.1 in the NHS policy states:
\begin{policyrule}{NHS}
  Downloading of personal apps onto a corporately issued mobile device should be avoided where possible. 
  The Trust would not encourage staff members to download apps for personal use onto a corporately issued mobile device.
  All staff are reminded that they must adhere to the guidance outlined in the Social Media Policy.
\end{policyrule}
The rule does not prohibit any action, and doesn't require the staff to do anything different.
It does remind staff to be aware of a rule which we could implement with an acknowledegement; a statement that the party has acknowledged a rule.
\begin{lstlisting}
'nhs-trust' says Staff:S mustAcknowledge('avoid-installing-personal-apps').
'nhs-trust' says Staff:S mustAcknowledge('social-media-policy').
\end{lstlisting}
In this case, however, since nothing is required even an acknowledgement seems excessive.
